Log Journal Project Theme 9

### 2022-10-24 LogJournal.Rmd
Moved the logjournal file

```{r}
# Read the file in ass a tibble
data <- as_tibble(read.table("yeast.data", sep = ""))
colnames(data) <- attr_names
head(data)
```

@@

```{r}
cat(readLines("data.arff", n = 15), sep = "\n")
```

@@

```{r}
weka.result <- read.table("Result.csv", header = TRUE, sep = ",")
# Remove weka.classifiers.* from classifier name
for (i in 1:length(weka.result$Key_Scheme)) {
  name <- weka.result$Key_Scheme[i]
  tweaked.name <- strsplit(name, split = ".", fixed = TRUE)[[1]][4]
  weka.result$Key_Scheme[i] <- tweaked.name
}
```

@@

![Ranking of chosen algorithms]("images/RankingAlgo.png")

@@

![Ranking of chosen algorithms by SD]("images/WekaSD.png")

@@

![Removed class difference]("images/WekaDataEdit.png")

@@

![Iterations ranked]("images/WekaIterRank.png")

@@

```{r, echo=FALSE}
tbl <- read.table("MetaResults.txt", header = TRUE)
colnames(tbl) <- c("Classifier", "TP Rate", "FP Rate", "Precision", "ROC Area", " ")
pander(tbl)
```

>>>>

```{r}
# Read the file in ass a tibble
data <- as_tibble(read.table("Resources/yeast.data", sep = ""))
colnames(data) <- attr_names
head(data)
```

@@

```{r}
cat(readLines("Resources/data.arff", n = 15), sep = "\n")
```

@@

```{r}
weka.result <- read.table("Resources/Result.csv", header = TRUE, sep = ",")
# Remove weka.classifiers.* from classifier name
for (i in 1:length(weka.result$Key_Scheme)) {
  name <- weka.result$Key_Scheme[i]
  tweaked.name <- strsplit(name, split = ".", fixed = TRUE)[[1]][4]
  weka.result$Key_Scheme[i] <- tweaked.name
}
```

@@

![Ranking of chosen algorithms]("Resources/images/RankingAlgo.png")

@@

![Ranking of chosen algorithms by SD]("Resources/images/WekaSD.png")

@@

![Removed class difference]("Resources/images/WekaDataEdit.png")

@@

![Iterations ranked]("Resources/images/WekaIterRank.png")

@@

```{r, echo=FALSE}
tbl <- read.table("Resources/MetaResults.txt", header = TRUE)
colnames(tbl) <- c("Classifier", "TP Rate", "FP Rate", "Precision", "ROC Area", " ")
pander(tbl)
```
